Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2020-01-14 2016-Weak-FH-Bisim/WeakBisim.tex
ajout fig

\paragraph{Example} Figure \ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet in Figure \ref{SimpleProt:Spec}. 
\RAB{Here, in the open automaton drawing, we use a user-friendly notation for the OTs, in the form ``$\{actions of holes\} [guard] action \{assigns\}$'', rather than the full OT form with the red-dotted rule. Note that the resulting action of the OTs appear here between the guard and the set of assignments. For examplein the upper left of the figure, the OT where $\beta=\{P\mapsto p\_a\}$, $\Pred=[\forall m. P\_a\neq p\_send(m)]$, and $\alpha=P\_a$ is denoted as ``\texttt{\{P->p-a\} [Forall m.P-a!=p-send(m)] P-a}''.
}

@@

@@

\begin{figure}[ht]
   \centerline{\includegraphics[width=10cm]{ATG/SPSpecWeakOpen}}
  \caption{Weak Open Automaton of the Specification \TODO{out of date}}
   \label{SimpleProtCounter:WeakSpecOA}
\end{figure}

\begin{figure}[t]
   \centerline{\includegraphics[width=12cm]{ATG/SPImplWeakOpen}}
  \caption{Weak Open Automaton of the implementation, \TODO{partial, can we show it in full ?}}
   \label{SimpleProtCounter:SpecOA-partial}
\end{figure}

>>>>

\paragraph{Example} Figure \ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet in Figure \ref{SimpleProt:Spec}. 
\RAB{Here, in the open automaton drawing, we use a user-friendly notation for the OTs, in the form ``$\{actions of holes\} [guard] action \{assigns\}$'', rather than the full OT form with the red-dotted rule. Note that the resulting action of the OTs appear here between the guard and the set of assignments. For example in the upper left of the figure, the OT where $\beta=\{P\mapsto p\_a\}$, $\Pred=[\forall m. P\_a\neq p\_send(m)]$, and $\alpha=P\_a$ is denoted as ``\texttt{\{P->p-a\} [Forall m.P-a!=p-send(m)] P-a}''.
}

@@

    \begin{figure}[ht]
  \centerline{\includegraphics[width=10cm]{XFIG/SPImplOpen}}
  \caption{Open Automaton of the Simple Protocol Implementation}  \label{SimpleProtCounter:ImplOA}
\end{figure}

@@

\begin{figure}[h]
   \centerline{\includegraphics[width=10cm]{ATG/SPSpecWeakOpen}}
  \caption{Weak Open Automaton of the Specification \TODO{out of date}}
   \label{SimpleProtCounter:WeakSpecOA}
\end{figure}

\begin{figure}[h]
   \centerline{\includegraphics[width=9cm]{XFIG/SimpleProtImpl-WOA}}
  \caption{Weak Open Automaton of the implementation}
   \label{SimpleProtCounter:SpecOA-partial}
\end{figure}

\TODO{Eric: insert here a table with the details of the WOTs...}

\smallskip
$1^st$ try, user-friendly style:

$$ 3 = \tau^*; \underline{in(m)}\{s1\_c:=0, s1\_m:=m\}; \tau\{s1\_c++\}^*$$

\smallskip
$2^nd$ try, full formal style ?:

$$ 1 = \openrule
         {\{P\mapsto\texttt{p-a}\}, [\forall m.p-a!=P\_send(m)], () }
         {000 \OTWeakarrow {\texttt{p-a}} 000}$$
\\
$$6 = \openrule
         {\{\}, [True], () }
         {100 \OTWeakarrow {\tau\big(\subst{m1\_c:=s1\_c,m1\_m:=s1\_m,s2\_c:=s1\_c}\subst{s1\_c:=s2\_c+1}\big)^* \subst{m1\_c:=s1\_c,m1\_m:=s1\_m,s2\_c:=s1\_c} } 210}
         $$
